---
title: "sales"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(data.table)
library(foreign)
sales <- data.table::fread('~/Dropbox/pkg.data/sales/raw/20142015 Comcast w SurveyQs Conf.csv')
spss <- foreign::read.spss('~/Dropbox/pkg.data/sales/raw/2014 2015 Comcast w  2015 Survey Qs Conf.sav')
```


# Sales project: Comcast Data

If I choose a goal level higher than one would predict then asymmetric information.
Here is asymmetric based on econometric modeling. Try to confirm or disconfirm the model.

Likelihood of achieving: 80\%

Likely_L4: Should be likelihood of baseline

Behavioral data: What they choose (likelihood): Survey data (likelihood of achieving each goal). Signals not only over confidence but asymmetric information.
Question of how hard they are going to work. If likelihood is 100\% but don't have to work that hard.

## 2014

1. Goal Selection
2. Performance Data

## 2015

1. Goal Selection

```{r}
pre.start <- which(names(sales)=='PreSurveyTaken')
pre.end <- which(names(sales)=='Gender')
pre.surveyFields <- names(sales)[pre.start:pre.end]
```

GoalLevel[2014,2015]
BaseObjective[2014, 2015]
GoalLevel/GoalLevel


2. Survey (Nothing about 2014 program)
    a. all names between PreSurveyTaken and Dups `r print(pre.surveyFields)`

All performance fields start before *PreSurveyTaken*

3. Performance data

4. Post Survey (If there was a 2016 program what is the likelihood of achieving you would take goal level 1,2,3 next time )
    a. PostEffort: The goal required a great amount of effort to achieve?
    b. PostEffortSatsf: Are you satisfied with the amount of effort you put in?
    b. PostGoalDiff: PostGoalDifficulty
    d. PostEffort: Did the goal require a great amount of effort to achieve?
    e. PostEffortBase[Lvl1, Lvl2, Lvl3]: How much effort would you need to put into to achieve
    f. PostLikeBase[Lvl1, Lvl2, Lvl3: What is the likelihood you will achieve (assuming the effort you would put in)
    


